Methods and Results

### 2022-10-05 ms.Rmd
Methods on Geary's test

We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta]. Given lnCVR makes certain assumptions about mean-variance relationships which are not always upheld [see @nakagawa2015meta], we also ran an arm-based analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model. See Supplement. Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR. Again, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).

>>>>

We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta]. Given lnCVR makes certain assumptions about mean-variance relationships, which are not always upheld [see @nakagawa2015meta], we also ran an 'arm-based' analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model. See Supplemental Materials for full details. Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR. Given lnCVR is a log ratio, we can only use ratio scale data to compute the effect size [@nakagawa2015meta]. In addition, data is assumed to be normally distributed; we tested this assumption using a modified Geary's test proposed by @laj2011. Only 6 effect sizes failed the test, and three of these were not ratio scale data. As such, we excluded this from our analysis. In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
